%%This is a very basic article template.
%%There is just one section and two subsections.
\documentclass{Article}
\usepackage{wasysym}

\begin{document}


\title{\bfseries{Room Mate Agreement}}
\author{Benjamin McLennan}
\maketitle

\centering{}
This Document is an agreement between all parties listed, for the set of rules\\
and guidelines set within this document. \\
They will uphold these rules and regulations to the best of their ability. \\

\newpage
\flushleft{}
\section{RoomMates:}
\begin{center}
\centerline
\itemize{}
\item Benjamin McLennan 
\item \rule{100pt}{1pt}
\item \rule{100pt}{1pt}
\item \rule{100pt}{1pt}
\end{center}
The above persons are herein referred collectively as ``roommates'' or,\\ individually as ``roommate''.\\ 	
\section{Terms:}
This agreement shall remain in effect from the day of signing until a \\
roommate terminates the agreement by voluntarily or involuntarily vacating.\\
The roommates will be released from the terms of the contract after he/she \\
vacates and has completed all responsibilities set forth in this agreement.\\
At this point the Roommate Agreement will be reviewed.

\section{Vacancy}
\subsection{Replacement}
If, for any reason a roommate vacates, they will attempt to find a suitable \\
replacement. If a substitute roommate is found, then the remaining roommates,\\
must approve of him/her.
\subsection{Notice}
A vacating roommate will give at least 30 days notice before leaving, so proper \\
arrangements can be made for locating a replacement, and the ejection of\\
personal items from the premises.
\subsection{Payment}
The roommate who is leaving is still obligated to pay the rent and bills that \\
are incurred during those 30 days, regardless of occupancy. 

\section{Security Deposit}
The security deposit of \$\rule{20pt}{1pt} has been paid in equal parts (\$\rule{20pt}{1pt} each)\\ 
by each roommate to the landlord. In the event a roommate is replaced,\\ 
the incoming roommate will pay the same portion of the deposit to the \\ 
outgoing roommate. In the event all roommates vacate at the same time \\
the rent will be split equally. In the event a replacement is not found, each \\
remaining roommate, will pay an equal amount to the vacating roommate to \\
refund his/her portion of the original deposit. \\
Deposits are forfeit in event of a forcible eviction / involuntary vacancy. Refer to the 
“Involuntary Vacancy” (Section \ref{invol}).\\
Deposits are also forfeit, if 30 days notice is not upheld.

\section{Rent}
Each roommate shall pay the following amount of rent:\\
\begin{tabbing}
Name             \rule{125pt}{0pt}\= Amount\\
\rule{100pt}{1pt} 				\>   \$\rule{20pt}{1pt}\\
\rule{100pt}{1pt} 				\>   \$\rule{20pt}{1pt}\\
\rule{100pt}{1pt} 				\>   \$\rule{20pt}{1pt}\\
\rule{100pt}{1pt} 				\>   \$\rule{20pt}{1pt}
\end{tabbing}

\section{Internet}
\subsection{Price}
The Amount per month for Internet is \$\rule{20pt}{1pt}. This will be spread equally among the house mates.

\subsection{Downloads}
Downloads larger than 2Gb will be downloaded in the offpeak time to be agreed upon by the roommates.
This may only be bypassed if agreed upon by the majority of roommates.



 









\section{Involuntary Vacancy}
\label{invol}

\subsection{Subtitle}

Plain text.
\Square
text.

\subsection{Another subtitle}

More plain text.


\end{document}
